---
title: "Preliminary results MBON_P2P SOURCE"
author: "Gonzalo Bravo"
date: "7/22/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, code=readLines("READ_DATA.R"), include=FALSE}
library(ggplot2)
```

# Objetives
- Test unsupervised configuration of the CoralNet software to identify CATAMI categories on intertidal photoquadrats from sampling sites of MBON.
- Provide a fast method to detect changes on intertidal habitats, using photoquadrats analysided by artificial intelligence (AI).

# Methods 
Photoquadrats from three locations with 90 quadrats per location were used for testing automated annotations form the CoralNet software and results were compared with visual quadrats. 

# Workflow 
1- 90 quadrats/site were visually inspected in situ with a 100 point grid ("Visualquadrat").

2- 90 photoquadrats/site were annotated by experts using a 100 points grid in CoralNet ("Human").

3- The 90 photoquadrats/site of point (1) were re-annotated by the experts using 100 random points. These annotations were used for training the automatic annotator of CoralNet using a diferent set of points than photoquadrats in point (2).

3- 90 photoquadrats/site were automatically annotated by the CoralNet robot using 100 points grid ("Robot").

4- 90 photoquadrats/site were annotated using the 50% alleviated mode of CoralNet robot. This modes annotates all the points in which the robot has a 50 % or higher level of confidence and the remaining points are annotaed by humans ("Alleviated 50%")

5- 90 photoquadrats/site were automatically annotated by the CoralNet robot using 100 points grid (same photos than in points 2 and 3) but using one independent robot for each site ("Robot.bycountry"). 

\pagebreak

# FUNCTIONAL GROUPS RESULTS
```{r plot1, echo=FALSE}
ggplot(Coverdata.FG,aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank()) + scale_fill_brewer(palette="Dark2")
```

```{r plot2, echo=FALSE}
ggplot(Coverdata.FG,aes(x=strata,y=cover.mean,fill=CATAMI)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW"))+ labs(fill = "CATAMI CODE",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + facet_grid(country~Comments) + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + scale_fill_brewer(palette="Dark2")
```


## CATAMI list
```{r CATAMIlistdefinition, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(labelset)
```

```{r plot3, echo=FALSE}
ggplot(Coverdata_abundant,aes(x=strata,y=cover.mean,fill=CATAMI)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW"))+ labs(fill = "CATAMI CODE",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + facet_grid(country~Comments) + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + scale_fill_brewer(palette="Dark2")
```

```{r plot4, echo=FALSE}
ggplot(Coverdata_abundant,aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="Dark2")
```


## BOXPLOT
```{r plot5, echo=FALSE}
ggplot(data=photoquadrat_visual_long.FG2, mapping=aes(x=strata, y=cover,fill=Comments)) +geom_boxplot()   + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="Dark2")
```

## COLOMBIA
```{r plot6, echo=FALSE}
ggplot(subset(Coverdata_abundant,country=="COLOMBIA"),aes(x=strata,y=cover.mean,fill=CATAMI)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW"))+ labs(fill = "CATAMI CODE",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + facet_grid(country~Comments) + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + scale_fill_brewer(palette="BrBG")

ggplot(subset(Coverdata_abundant,country=="COLOMBIA"& CATAMI!="MOB" & CATAMI!="MAS" & CATAMI!="MAA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```


## ECUADOR
```{r plot7, echo=FALSE}
ggplot(subset(Coverdata_abundant,country=="ECUADOR"),aes(x=strata,y=cover.mean,fill=CATAMI)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW"))+ labs(fill = "CATAMI CODE",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + facet_grid(country~Comments) + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + scale_fill_brewer(palette="BrBG")

ggplot(subset(Coverdata_abundant,country=="ECUADOR"& CATAMI!="MOB" & CATAMI!="MAS" & CATAMI!="MAA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```

## ARGENTINA
```{r plot8, echo=FALSE}
ggplot(subset(Coverdata_abundant,country=="ARGENTINA"),aes(x=strata,y=cover.mean,fill=CATAMI)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW"))+ labs(fill = "CATAMI CODE",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + facet_grid(country~Comments) + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + scale_fill_brewer(palette="BrBG")

ggplot(subset(Coverdata_abundant,country=="ARGENTINA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```

\pagebreak


# Code and data files 
All the codes and data files are in github

https://github.com/gonzalobravoargentina/CoralNet_MBON
