---
title: "Results MBON_CORALNET"
author: "Gonzalo Bravo"
date: "8/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, code=readLines("READ_DATA.R"), include=FALSE}
library(ggplot2)
```

# Objetives
- Test unsupervised configuration of the CoralNet software to identify CATAMI categories on intertidal photoquadrats from sampling sites of MBON.
- Provide a fast method to detect changes on intertidal habitats, using photoquadrats analysided by artificial intelligence (AI).

# Methods 
Photoquadrats from 4 locations with 90 quadrats per location were used for testing automated annotations form the CoralNet software and results were compared with visual quadrats. 

# Workflow 
1- 90 quadrats/site were visually inspected in situ with a 100 point grid ("Visualquadrat").

2- 90 photoquadrats/site were annotated by experts using a 100 points grid in CoralNet ("Human").

3- The 90 photoquadrats/site of point (1) were re-annotated by the experts using 100 random points. These annotations were used for training the automatic annotator of CoralNet using a diferent set of points than photoquadrats in point (2).

3- 90 photoquadrats/site were automatically annotated by the CoralNet robot using 100 points grid ("Robot").

4- 90 photoquadrats/site were automatically annotated by the CoralNet robot using 100 points grid (same photos than in points 2 and 3) but using one independent robot for each site ("Robot.bycountry"). 

\pagebreak

# FUNCTIONAL GROUPS RESULTS
```{r plot1, echo=FALSE,fig.height = 10, fig.width = 10, fig.align = "center"}
ggplot(Coverdata.FG,aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank()) + scale_fill_brewer(palette="Dark2")
```

\pagebreak

## CATAMI list
```{r CATAMIlistdefinition, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(labelset)
```


```{r plot4, echo=FALSE, fig.height = 10, fig.width = 10, fig.align = "center"}
ggplot(Coverdata_abundant,aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="Dark2")
```

\pagebreak

## BOXPLOT
```{r plot5, echo=FALSE,fig.height = 10, fig.width = 10, fig.align = "center"}
ggplot(data=photoquadrat_visual_long.FG, mapping=aes(x=strata, y=cover,fill=Comments)) +geom_boxplot()   + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="Dark2")
```

\pagebreak

## COLOMBIA
```{r plot6, echo=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
ggplot(subset(Coverdata_abundant,country=="COLOMBIA"& CATAMI!="MOB" & CATAMI!="MAS" & CATAMI!="MAA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```


## ECUADOR
```{r plot7, echo=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
ggplot(subset(Coverdata_abundant,country=="ECUADOR"& CATAMI!="MOB" & CATAMI!="MAS" & CATAMI!="MAA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```

\pagebreak

## ARGENTINA
```{r plot8, echo=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
ggplot(subset(Coverdata_abundant,country=="ARGENTINA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```

## USA
```{r plot9, echo=FALSE, fig.height = 5, fig.width = 10, fig.align = "center"}
ggplot(subset(Coverdata_abundant,country=="USA"),aes(x=strata,y=cover.mean,fill=Comments)) + geom_bar(alpha=0.7,stat="identity",color="black",position=position_dodge()) + scale_color_grey() + geom_errorbar(aes(ymin=cover.mean-cover.SE, ymax=cover.mean+cover.SE), width=.2,position=position_dodge(.9)) + theme_bw() + scale_y_continuous(limits = c(0,100))+ scale_x_discrete(limits=c("HIGHTIDE","MIDTIDE","LOWTIDE"),labels=c("HIGH","MID","LOW")) + facet_grid(country~CATAMI) + labs(fill = "Method",x = "", y = "Cover (%)", title = "",caption ="Mean + SE") + theme(legend.position = "bottom",panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank())  + scale_fill_brewer(palette="BrBG")
```

\pagebreak

## Methods comparations

```{r correlations, include=FALSE}
library(ggpubr) 
```

```{r plot11, echo=FALSE, fig.height=4, fig.width=6, message=FALSE, warning=FALSE}
ggscatter(correlations, x = "SC.H", y = "SC.A", add = "reg.line",conf.int=T) +
  labs(title="SC", y="Photo",x="Visual")+ ylim(0,100)+ xlim(0,100)+
  stat_cor(label.x = 3, label.y = 100)
```

```{r correlations2, include=FALSE}
library(gridExtra)
library(gridGraphics)
library(cowplot)
site <- correlations$country.A

#by photo
SC<-  summaryBy(SC.A + SC.H  ~ Name ,data=correlations , FUN = mean)
SC$site <- site
#differenced_data= Method_A - Method_B
SC$diff <- SC$SC.A.mean-SC$SC.H.mean
SC$avg <- (SC$SC.A.mean + SC$SC.H.mean) / 2

#by site
SC2<-  summaryBy(SC.A + SC.H ~ country.A ,data=correlations, FUN = mean)
SC2$diff <- SC2$SC.A.mean-SC2$SC.H.mean
SC2$avg <- (SC2$SC.A.mean + SC2$SC.H.mean) / 2

#plot by photo
g1 <- ggplot(SC, aes(x=avg, y=diff,colour=site))+geom_hline(yintercept=0) + geom_point()+ theme_bw()+labs(y="Difference in % cover between methods", x="",title = "Substrate Consolidate")+theme(legend.position="none",plot.margin=unit(c(0,0,1,1), "cm"))
#plot by site
g2 <- ggplot(SC2, aes(x=avg, y=diff,colour=country.A)) + geom_point()+theme_bw() + labs(y="", x="Avg % cover of both methods (± 95%CI)") + theme(axis.title.y =element_blank(),axis.text.y=element_blank(),axis.ticks.y=element_blank())+geom_hline(yintercept=0)+theme(legend.position="none",plot.margin=unit(c(0,1,1,-0.1), "cm"))+geom_errorbar(aes(ymin =c(-9.211,2.567,5.622),ymax =c(-2.978,10.746,12.367)),width = 0.2) + geom_errorbarh(aes(xmin = c(21.56,70.47,80.63),xmax = c(34.56,81.63,89.20)),height =-.2)

#set y limits and brecks
limits <- c(-30, 90)
breaks <- seq(limits[1], limits[2], by=8)

# assign common axis to both plots
p1.common.y <- g1 + scale_y_continuous(limits=limits, breaks=breaks)
p2.common.y <- g2 + scale_y_continuous(limits=limits, breaks=breaks)

# At this point, they have the same axis, but the axis lengths are unequal, so ...
# build the plots 
p1.common.y <- ggplot_gtable(ggplot_build(p1.common.y))
p2.common.y <- ggplot_gtable(ggplot_build(p2.common.y))

# copy the plot height from p1 to p2
p2.common.y$heights <- p1.common.y$heights
#plot grid
grid <- grid.arrange(p1.common.y,p2.common.y,ncol=2,widths=c(1,1))

#add legend
legend <- ggplot(SC, aes(x=avg, y=diff,colour=site))+geom_hline(yintercept=0) + geom_point()+ theme_bw()+labs(y="Difference in % cover between methods", x="% cover visual",title = "Bare Substrate")+theme(legend.position="top",plot.margin=unit(c(0,0,1,1), "cm"))
legend_plot <- get_legend(legend)#take legend

```

```{r plot12, echo=FALSE, message=FALSE, warning=FALSE,fig.height = 5, fig.width = 6}
plot_grid(legend_plot,grid, ncol = 1, rel_heights = c(.1,1))
```



# Code and data files 
All the codes and data files are in github

https://github.com/gonzalobravoargentina/CoralNet_MBON
