---
title: "Photoquadrats"
author: 'E. Klein'
date: "20210617"
output: 
  html_document:
    toc:  TRUE
    toc_float: TRUE
    toc_depth: 5
    theme: spacelab
    highlight: kate
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, cache = F, echo = F, message = F, warning = F, tidy = F}
# make this an external chunk that can be included in any file
require(knitr)
options(width = 100)
opts_chunk$set(echo =T, message = F, error = F, warning = F, comment = NA,  
               fig.align = 'left',  fig.width = 7.5, fig.height = 6,
               tidy = F, cache.path = '.cache/', fig.path = 'fig/')
               
library(RColorBrewer)
palette(brewer.pal(8, "Set2"))


## load packages
library(readr)
library(ggplot2)
library(ggpubr)
library(kableExtra)
library(patchwork)

library(caret)
library(vegan)

library(stringr)
library(tidyr)
library(dplyr)
library(forcats)

library(lme4)
library(multcomp)

library(formattable)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)


## data sources
robotDir <- "../Source_MBON_AR_CO_EC_US_Robot/New"
humanDir <- "../Source_MBON_AR_CO_EC_US_Human/New"
confmatDir <- "../confusion_matrix"
cleandataDir <- "../DataClean"
```

last run `r Sys.time()`



# Goals

This document evaluates the performance of the CoralNet to classify rocky shores main groups from photoquadrats

The analysis comprises:

2.  Compare the classification results of the visually identified quadrats with automatic classification of photoquadrats

# Data

The data is available at [CoralNet_MBON Github repository](https://github.com/gonzalobravoargentina/CoralNet_MBON). The codes for doing the analysis could be found the the Code directory of the same repo.


# Labels

Human labelled photoquadrats were used as a training input for the CoralNet classifier. A total of 360 pictures with 100 rectagular grid of points were annotated using the following labels:

```{r}
labelset <- read.csv("../Labelset/labelset_used.csv")

kable(labelset) %>% kable_styling("striped")

```

Proportion of the labels in the set

```{r}
df <- read.csv(file.path(robotDir, "annotations.csv"))
dfHuman <- df %>% filter(Comments=='random')
dfRobot <- df %>% filter(Comments=='robot')
dfSummary <- dfHuman %>% group_by(Label) %>% 
  summarise(nPoints = n(), Countries = paste0(unique(country), collapse = ", ")) %>% 
  mutate(Percent = round(100*nPoints/nrow(df),1)) %>% 
  arrange(-nPoints)
dfSummary <- left_join(dfSummary, labelset[,c('Name', 'Short.Code')], by=c('Label'='Short.Code')) %>% 
  relocate(Name, Label, nPoints, Percent, Countries)

formattable(dfSummary, list(Percent=color_bar("steelblue")))
```

As functional groups the labels and its representation in the data set:

```{r}
dfFuncGroup <- left_join(df, labelset[,c('Functional.Group', 'Short.Code')], by=c('Label'='Short.Code') )
dfSummary <- dfFuncGroup %>% group_by(Functional.Group) %>% 
  summarise(nPoints = n(), Countries = paste0(unique(country), collapse = ", ")) %>% 
  mutate(Percent = round(100*nPoints/nrow(df),1)) %>% 
  relocate(Functional.Group, nPoints, Percent, Countries) %>% 
  arrange(-nPoints)

formattable(dfSummary, list(Percent=color_bar("steelblue")), caption="Functional groups label set")
```


# Full Community

## Photoquadrats vs Robot


This compares the classification of the 100 point grid labels from the photo quadrats to the output of the robot. We will use the same Bray-Curtis approach as we're interested in the composition of the community. If the robot is good enough, the BC distance must remain close to zero in the majority of the quadrats.

We will use the labels that contribute in total up to 95% of all the records. The reason behind this is that with few rare labels used in the training of the robot, the classification accuracy of these labels are expected to be low, hence producing an artificially higher Bray-Curtis distance.

```{r}
## get fotoquadrat human community data
CM_HumanRobot <- read.csv(file.path(cleandataDir, "DF_HumanRobot.csv"))
humanLabels <- CM_HumanRobot %>% filter(source=="human") %>% 
  group_by(Label) %>% 
  summarise(n=sum(Cover)) %>% 
  arrange(-n) %>% 
  mutate(acum=cumsum(n), acumP = acum/sum(n))
humanLabels95 <- humanLabels$Label[humanLabels$acumP<=0.96]                                                  

## make community matrix from robot
robotLabels <- CM_HumanRobot %>% filter(source=="robot") %>% 
  group_by(Label) %>% 
  summarise(n=sum(Cover)) %>% 
  arrange(-n) %>% 
  mutate(acum=cumsum(n), acumP = acum/sum(n))
robotLabels95 <- robotLabels$Label[robotLabels$acumP<=0.96]                                                  

## intersect the set of both labels and use only 95% labels
labels95 <- intersect(humanLabels95, robotLabels95)
CM_HumanRobot95 <- CM_HumanRobot %>% filter(Label %in% labels95)

## make it wide
CM_HumanRobot95_wide <- CM_HumanRobot95 %>% pivot_wider(id_cols = Name:strata, names_from = 'Label', values_from = 'Cover')
CM_HumanRobot95_wide[is.na(CM_HumanRobot95_wide)] <- 0
CM_Human95 <- CM_HumanRobot95_wide %>% filter(source=="human")
CM_Robot95 <- CM_HumanRobot95_wide %>% filter(source=="robot")
```


Generate the BC table. For each photo (Name) build a two-row community matrix (row1: Human, row2: Robot), and calculate the BC distance.

```{r}
## calculate BC index
BC_RH <- data.frame(Name=character(), BC=numeric())
nLabels <- ncol(CM_Human95)
for (i in 1:nrow(CM_Human95)){
  robotIndex <- which(CM_Robot95$Name==CM_Human95$Name[i])
  if (length(robotIndex) > 0 ){
    CM_one <- bind_rows(CM_Human95[i,6:nLabels], CM_Robot95[robotIndex,6:nLabels])
    CM_one[is.na(CM_one)] <- 0
    BC_RH <- bind_rows(BC_RH, 
                    data.frame(Name = CM_Human95$Name[i],
                               BC = as.numeric(vegdist(CM_one, na.rm = T))))
  }else {
    print(paste0("NOT FOUND in Robot: ", CM_Visual$Name[i]))
  }
}

## fix the mess US did with the Human and Robot Name (that sounds deep, very deep!)
BC_RH$Country <- str_sub(BC_RH$Name,1,2)
BC_RH$Site <- ifelse(BC_RH$Country=='US', str_sub(BC_RH$Name,3,6),str_split(BC_RH$Name, "_", simplify = T)[,3] )
BC_RH$Strata <- ifelse(BC_RH$Country=='US', str_split(BC_RH$Name, "_", simplify = T)[,3],
                            str_split(BC_RH$Name, "_", simplify = T)[,4])
BC_RH$Strata <- recode_factor(BC_RH$Strata, low="MT", high="HT")


## recode locations
BC_RH$Site <- recode_factor(BC_RH$Site, PC="Punta Cuevas", PE="Punta Este", PL="Punta Lobos", 
                            LM="La Mancora", LV="La Ventana", PV="Playa Verde", 
                            CD="Charles Darwin Station", RA="Ratonera", TO="Tortuga Bay", 
                            MAMH="MAMH", MAPH="MAPH", MECH="MECH", MEGS="MEGS")
BC_RH$Strata <- recode_factor(BC_RH$Strata, LT="LOWTIDE", MT="MIDTIDE", HT="HIGHTIDE")

```

Summarise the BS distances by groups

```{r}
BCsummary <- BC_RH %>% group_by(Strata) %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75), 
            BCmin = min(BC), 
            BCmax = max(BC))

kable(BCsummary, digits=3, caption = "All labels: HUMAN vs ROBOT") %>% kable_styling("striped")


BCsummaryGlobal <- BC_RH %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummaryGlobal, digits=3, caption = "All Labels: HUMAN vs ROBOT global BC stats") %>% kable_styling("striped")
```


Plot the BC distances by strata and country:

```{r}

strataColor = c(LOWTIDE="#f7fcb9", MIDTIDE="#addd8e", HIGHTIDE="#31a354")

pp_ARG <- ggplot(BC_RH %>% filter(Country=="AR"), aes(Strata, BC))
pp_ARG <- pp_ARG + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) +
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ARGENTINA", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_COL <- ggplot(BC_RH %>% filter(Country=="CO"), aes(Strata, BC))
pp_COL <- pp_COL + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="COLOMBIA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ECU <- ggplot(BC_RH %>% filter(Country=="EC"), aes(Strata, BC))
pp_ECU <- pp_ECU + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ECUADOR", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_USA <- ggplot(BC_RH %>% filter(Country=="US"), aes(Strata, BC))
pp_USA <- pp_USA + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="USA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

(pp_ARG + pp_COL) / (pp_ECU + pp_USA)


```

```{r}
pp <- ggplot(BC_RH, aes(Country, BC, fill=Strata))
pp + geom_boxplot(position=position_dodge2(preserve = "single"), aes(fill=Strata), outlier.size = 0.3, lwd=0.2) + 
  labs(x="", y="Bray-Curtis distance") +
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  theme_pubclean()
```


Let's try another version

```{r}
pp <- ggplot(BC_RH, aes(Country, BC, fill=Strata))
pp + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", position=position_dodge2(preserve="single") , outlier.size = 0.3, lwd=0.2) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  ylim(0, 0.3) + 
  labs(x="", y="Bray-Curtis Distance") + 
  facet_grid(~Strata) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

```

Apply a GMM nested model 

It is a bit tricky as it is not balanced: US has four (4) sites, the rest three (3),  and also sampled the HT and LT but not MT. So the model is strata nested in country with quadrat aas random factor

```{r}

BC_RH <- BC_RH %>% 
  group_by(Country, Site, Strata) %>% 
  mutate(Quadrat=1:n()) 

model = glmer(BC ~ Country + Strata + Country*Strata + (1|Site/Quadrat), data=BC_RH, family=binomial)
summary(model)

#model_glm <- glm(BC ~ Country*Strata, data=BC_RH, family=binomial)
#summary(model_glm)

testCountry = glht(model, linfct = mcp(Country = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```


There is no sig differences between the estimates of community composition between strata or countries. 


```{r}
BCmean <- round(mean(BC_RH$BC),3)
BCn <- nrow(BC_RH)
BCsd <- sd(BC_RH$BC)
BCmargin <- qt(0.975,df=BCn-1)*BCsd/sqrt(BCn)
BCupper <- round(BCmean + BCmargin, 3)
BClower <- round(BCmean - BCmargin, 3) 

```

As demonstrated, the classifier is insensitive to the variability produced by Country and Strata, being equally efficient no matter the source of the quadrat. **In general, the difference between the classifier and the visual estimate of the community cover of a mean quadrat is `r BCmean` with a 95% confidence interval of [`r BClower` - `r BCupper`]**





## Similarity with visual

The idea here is to test if there is differences between the quadrat surveyed in the field and analysed visually with the result of the classifier over the same quadrats.

As we don't label every point in the quadrat in the field, it is not possible to make a point-to-point comparison. However, if we estimate the cover of each of the categories in each of the quadrats and do the same with the result of the classifier, it will be possible to calculate a distance metric that represent how different are the estimates. AS we are dealing with counts (number of points in each category), a Bray-Curtis distance is appropriate. Here the hypothesis is that if both methods produce the same result, the BC distance must be zero.

For each quadrat it is possible to make a community matrix: 2 rows, visual and machine estimates, and n columns, being n the number of labels). Then we can calculate the BC distance comparing the two methods.

Then we can compare the BC distances (as proportions) using a generalized nested mixed models.

Method:

1.  bind visual cover estimates from all sites, except USA, as the USA photoquadrats does not coincide with the quadrats used for visual estimates

```{r}
## it may be repeated but letś do it again in case we want to do a separate analysis
## get Visual data
CM_Visual <- read_csv(file.path(cleandataDir, "CM_visual.csv"), col_types = cols())
CM_Robot <- read_csv(file.path(cleandataDir, "CM_robot.csv"), col_types = cols())

##match the robot labels to visual labels
labelsVisual <- colnames(CM_Visual)[6:ncol(CM_Visual)]
CM_Robot <- CM_Robot %>% dplyr::select(Name:strata,  contains(labelsVisual))

## replace NA by zero
CM_Visual[is.na(CM_Visual)] <- 0
CM_Robot[is.na(CM_Robot)] <- 0
```

#### Full Label Set

We will use the only the labels produced by the classifier as the label set. We will drop not used labels from the visual and recalculate the cover.

```{r}
## calculate BC index
nLabels <- ncol(CM_Visual)

BC_VR <- data.frame(Country=character(), Site=character(), Strata=character(), BC=numeric())
for (i in 1:nrow(CM_Visual)){
  robotIndex <- which(CM_Robot$Name==CM_Visual$Name[i])
  if (length(robotIndex) > 0 ){
    CM_one <- bind_rows(CM_Visual[i,6:nLabels], CM_Robot[robotIndex,6:nLabels])
    CM_one[is.na(CM_one)] <- 0
    BC_VR <- bind_rows(BC_VR, 
                    data.frame(Country = CM_Visual$country[i],
                               Site = CM_Visual$site[i],
                               Strata = CM_Visual$strata[i],
                               BC = as.numeric(vegdist(CM_one, na.rm = T))))
  }else {
    print(paste0("NOT FOUND in Robot: ", CM_Visual$Name[i]))
  }
}
BC_VR$Site <- recode_factor(BC_VR$Site, PC="Punta Cuevas", PE="Punta Este", PL="Punta Lobos", 
                            LM="La Mancora", LV="La Ventana", PV="Playa Verde", 
                            CD="Charles Darwin Station", RA="Ratonera", TO="Tortuga Bay", 
                            MAMH="MAMH", MAPH="MAPH", MECH="MECH", MEGS="MEGS")
BC_VR$Strata <- factor(BC_VR$Strata, levels = c("LT", "MT", "HT"), labels = c("LOWTIDE", "MIDTIDE", "HIGHTIDE"))
BC_VR$Country <- factor(BC_VR$Country, levels = c("AR", "CO", "EC"), labels = c("ARGENTINA", "COLOMBIA", "ECUADOR"))

```

Summarise the BS distances by groups

```{r}
BCsummary <- BC_VR %>% group_by(Strata) %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummary, digits=3, caption = "All labels: VISUAL vs. ROBOT") %>% kable_styling("striped")

BCsummaryGlobal <- BC_VR %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummaryGlobal, digits=3, caption = "All Labels: VISUAL vs ROBOT global BC stats") %>% kable_styling("striped")
```



```{r, fig.height=12}
pp_ARG <- ggplot(BC_VR %>% filter(Country=="ARGENTINA"), aes(Strata, BC))
pp_ARG <- pp_ARG + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ARGENTINA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_COL <- ggplot(BC_VR %>% filter(Country=="COLOMBIA"), aes(Strata, BC))
pp_COL <- pp_COL + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="COLOMBIA", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ECU <- ggplot(BC_VR %>% filter(Country=="ECUADOR"), aes(Strata, BC))
pp_ECU <- pp_ECU + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ECUADOR", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ARG / pp_COL / pp_ECU


```

#### Reduced Label Set

Let's try to reduce the number of labels to the most representative ones. It makes sense as the infrequent labels have poorly accuracy in the classifier as the number of training points is very low.

Try with the labels that are present in 99.5% of the points in the Visual file:

This is the number of points and accumulated % per label:

```{r}
DF_VisualRobot <- read_csv(file.path(cleandataDir, "DF_VisualRobot.csv"), col_types = cols())

labelTable <- DF_VisualRobot %>% group_by(Label) %>% 
  summarise(VISUAL = sum(Cover[source=='visual']), ROBOT = sum(Cover[source=='robot'])) %>% 
  arrange(-VISUAL) %>% 
  mutate(VISUALcum = round(100*cumsum(VISUAL)/sum(VISUAL),2), 
         ROBOTcum = round(100*cumsum(ROBOT)/sum(ROBOT),2))

kable(labelTable) %>% kable_styling("striped")
labels995 <- labelTable$Label[labelTable$VISUALcum <= 99.6]
```

The labels that accumulate up to 99.6% of the points are:

```{r}
cat(labels995)
```


and repeat the BC analysis, including only **`r paste0(labels95, collapse=",")`**...

```{r}
## Filter robot labels using selected visual labels
CM_Robot995 <- CM_Robot %>% dplyr::select(Name:strata, contains(labels995))
CM_Visual995 <- CM_Visual %>% dplyr::select(Name:strata, contains(labels995))

## calculate BC index
BC_VR995 <- data.frame(Country=character(), Site=character(), Strata=character(), BC=numeric())
for (i in 1:nrow(CM_Visual995)){
  robotIndex <- which(CM_Robot995$Name==CM_Visual995$Name[i])
  if (length(robotIndex) > 0 ){
    CM_one <- bind_rows(CM_Visual995[i,6:ncol(CM_Visual995)], CM_Robot995[robotIndex,6:ncol(CM_Robot995)])
    CM_one[is.na(CM_one)] <- 0
    BC_VR995 <- bind_rows(BC_VR995, 
                    data.frame(Country = CM_Visual995$country[i],
                               Site = CM_Visual995$site[i],
                               Strata = CM_Visual995$strata[i],
                               BC = as.numeric(vegdist(CM_one, na.rm = T))))
  }else {
    print(paste0("NOT FOUND in Robot: ", CM_Visual$Name[i]))
  }
}
BC_VR995$Site <- recode_factor(BC_VR995$Site, PC="Punta Cuevas", PE="Punta Este", PL="Punta Lobos", 
                            LM="La Mancora", LV="La Ventana", PV="Playa Verde", 
                            CD="Charles Darwin Station", RA="Ratonera", TO="Tortuga Bay", 
                            MAMH="MAMH", MAPH="MAPH", MECH="MECH", MEGS="MEGS")
BC_VR995$Strata <- factor(BC_VR995$Strata, levels = c("LT", "MT", "HT"), labels = c("LOWTIDE", "MIDTIDE", "HIGHTIDE"))
BC_VR995$Country <- factor(BC_VR995$Country, levels = c("AR", "CO", "EC"), labels = c("ARGENTINA", "COLOMBIA", "ECUADOR"))
```

Summarise the BS distances by groups

```{r}
BCsummary <- BC_VR995 %>% group_by(Strata) %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummary, digits=3, caption = "All labels: VISUAL vs. ROBOT") %>% kable_styling("striped")

## global stats
BCsummaryGlobal <- BC_VR995 %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummaryGlobal, digits=3, caption = "95% Labels: VISUAL vs ROBOT global BC stats") %>% kable_styling("striped")
```




```{r, fig.height=12}
pp_ARG <- ggplot(BC_VR995 %>% filter(Country=="ARGENTINA"), aes(Strata, BC))
pp_ARG <- pp_ARG + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ARGENTINA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_COL <- ggplot(BC_VR995 %>% filter(Country=="COLOMBIA"), aes(Strata, BC))
pp_COL <- pp_COL + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="COLOMBIA", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ECU <- ggplot(BC_VR995 %>% filter(Country=="ECUADOR"), aes(Strata, BC))
pp_ECU <- pp_ECU + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.8) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ECUADOR", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ARG / pp_COL / pp_ECU


```


Let's try another version

```{r}
pp <- ggplot(BC_VR995, aes(Country, BC, fill=Strata))
pp + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", position=position_dodge2(preserve="single") , outlier.size = 0.3, lwd=0.2) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  ylim(0, 0.3) + 
  labs(x="", y="Bray-Curtis Distance") + 
  facet_grid(~Strata) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

```



Description of the BC values

```{r}
BCsummary <- BC_VR995 %>% group_by(Country, Site, Strata) %>% 
  summarize(n = n(), BCmean = mean(BC), BCsd = sd(BC), BCmin = min(BC), BCmax = max(BC),
            BCq25 = quantile(BC, 0.25), BCmedian = median(BC), BCq75 = quantile(BC, 0.75))

kable(BCsummary, digits=2) %>% kable_styling("striped", full_width = FALSE)
```

#### Nested model

Let's create additional variables: Quadrat and Site2 which are the sites coded as A, B, C

```{r}

BC_VR995$Quadrat <- rep(1:10, 27)
BC_VR995$Site2 <- rep(c(rep("A",30), rep("B", 30), rep("C", 30)), 3)
```

and fit a binomial nested model with BC as dependent variables and Country, Site and Strata as fixed factors and Quadrat as random factor.

```{r}
library(lme4)
library(multcomp)

par(mar=c(7,7,7,7))
par(oma=c(1,1,1,1))

model = glmer(BC ~ Country + Strata + Country*Strata + (1|Site/Quadrat), data=BC_VR995, family=binomial)
summary(model)

testStrata = glht(model, linfct = mcp("Strata" = "Tukey"))
summary(testStrata)
plot(confint(testStrata), cex=0.5)

testCountry = glht(model, linfct = mcp("Country" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```

```{r}
BCmean <- round(mean(BC_VR995$BC),3)
BCn <- nrow(BC_VR995)
BCsd <- sd(BC_VR995$BC)
BCmargin <- qt(0.975,df=BCn-1)*BCsd/sqrt(BCn)
BCupper <- round(BCmean + BCmargin, 3)
BClower <- round(BCmean - BCmargin, 3) 

```

AS demonstrated, the classifier is insensitive to the variability produced by Country, Site and Strata, being equally efficient no matter the source of the quadrat. **In general, the difference between the classifier and the visual estimate of the community cover of a mean quadrat is `r BCmean` with a 95% confidence interval of [`r BClower` - `r BCupper`]**








# Functional groups


According to Gonza's code the correspondence of `labels` to `funcGroup` is:

| Functional Group | Label                                     |
|------------------|-------------------------------------------|
| `ALGAE`          | MAF,MAEN,MAA,MAG,MAS,MALCB,MAEC,MAEF,MALA |
| `SUBSTRATE`      | SC                                        |
| `INVERTEBRATES`  | CRB,MOB,CNTR,WPOT,MOG,CNCA,BRY,CR,MOCH    |



### Human vs Robot

```{r}
DF_FG_HumanRobot <- read_csv(file.path(cleandataDir, "DF_FG_HumanRobot.csv"), col_types = cols())

CM_FG_Human <- DF_FG_HumanRobot %>% filter(source=='human') %>% 
  pivot_wider(names_from = 'Label', values_from = 'Cover')

CM_FG_Robot <- DF_FG_HumanRobot %>% filter(source=='robot') %>% 
  pivot_wider(names_from = 'Label', values_from = 'Cover')

```


Calculate Bray-Curtis

```{r}
## calculate BC index
nLabels <- ncol(CM_FG_Human)

BC_FGHR <- data.frame(Country=character(), Site=character(), Strata=character(), BC=numeric())
for (i in 1:nrow(CM_FG_Human)){
  robotIndex <- which(CM_FG_Robot$Name==CM_FG_Human$Name[i])
  if (length(robotIndex) > 0 ){
    CM_one <- bind_rows(CM_FG_Human[i,6:nLabels], CM_FG_Robot[robotIndex,6:nLabels])
    CM_one[is.na(CM_one)] <- 0
    BC_FGHR <- bind_rows(BC_FGHR, 
                    data.frame(Country = CM_FG_Human$country[i],
                               Site = CM_FG_Human$site[i],
                               Strata = CM_FG_Human$strata[i],
                               BC = as.numeric(vegdist(CM_one, na.rm = T))))
  }else {
    print(paste0("NOT FOUND in Robot: ", CM_FG_Human$Name[i]))
  }
}
BC_FGHR$Site <- recode_factor(BC_FGHR$Site, PC="Punta Cuevas", PE="Punta Este", PL="Punta Lobos", 
                            LM="La Mancora", LV="La Ventana", PV="Playa Verde", 
                            CD="Charles Darwin Station", RA="Ratonera", TO="Tortuga Bay", 
                            MAMH="MAMH", MAPH="MAPH", MECH="MECH", MEGS="MEGS")
BC_FGHR$Strata <- factor(BC_FGHR$Strata, levels = c("LT", "MT", "HT"), labels = c("LOWTIDE", "MIDTIDE", "HIGHTIDE"))
BC_FGHR$Country <- factor(BC_FGHR$Country, levels = c("AR", "CO", "EC", "US"), labels = c("ARGENTINA", "COLOMBIA", "ECUADOR", "USA"))

```

Summarise the BS distances by groups

```{r}
BCsummary <- BC_FGHR %>% group_by(Strata) %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummary, digits=3, caption = "Functional groups: HUMAN vs. ROBOT") %>% kable_styling("striped")

## global stats
BCsummaryGlobal <- BC_FGHR %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummaryGlobal, digits=3, caption = "Functional groups: Human vs Robot global BC stats") %>% kable_styling("striped")
```



PLOTs

```{r}
pp_ARG <- ggplot(BC_FGHR %>% filter(Country=="ARGENTINA"), aes(Strata, BC))
pp_ARG <- pp_ARG + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) +
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ARGENTINA", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_COL <- ggplot(BC_FGHR %>% filter(Country=="COLOMBIA"), aes(Strata, BC))
pp_COL <- pp_COL + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="COLOMBIA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ECU <- ggplot(BC_FGHR %>% filter(Country=="ECUADOR"), aes(Strata, BC))
pp_ECU <- pp_ECU + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ECUADOR", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_USA <- ggplot(BC_FGHR %>% filter(Country=="USA"), aes(Strata, BC))
pp_USA <- pp_USA + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="USA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

(pp_ARG + pp_COL) / (pp_ECU + pp_USA)
```


Let's try another version

```{r}
pp <- ggplot(BC_FGHR, aes(Country, BC, fill=Strata))
pp + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", position=position_dodge2(preserve="single") , outlier.size = 0.3, lwd=0.2) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  ylim(0, 0.3) + 
  labs(x="", y="Bray-Curtis Distance") + 
  facet_grid(~Strata) + 
  theme_pubclean()

```


GMM model 

```{r}
BC_FGHR <- BC_FGHR %>% group_by(Country, Site, Strata) %>% mutate(Quadrat = seq_len(n()))


model = glmer(BC ~ Country + Strata + Country*Strata + (1|Site/Quadrat), data=BC_FGHR, family=binomial)
summary(model)

testStrata = glht(model, linfct = mcp("Strata" = "Tukey"))
summary(testStrata)
plot(confint(testStrata), cex=0.5)

testCountry = glht(model, linfct = mcp("Country" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```

```{r}
BCmean <- round(mean(BC_FGHR$BC),3)
BCn <- nrow(BC_FGHR)
BCsd <- sd(BC_FGHR$BC)
BCmargin <- qt(0.975,df=BCn-1)*BCsd/sqrt(BCn)
BCupper <- round(BCmean + BCmargin, 3)
BClower <- round(BCmean - BCmargin, 3) 

```

AS demonstrated, the classifier is insensitive to the variability produced by Country, Site and Strata, being equally efficient no matter the source of the quadrat. **In general, the difference between the classifier and the visual estimate of the photocuadrat cover of a mean quadrat is `r BCmean` with a 95% confidence interval of [`r BClower` - `r BCupper`]**





### Visual vs Robot

```{r}
DF_FG_VisualRobot <- read_csv(file.path(cleandataDir, "DF_FG_VisualRobot.csv"), col_types = cols())

CM_FG_Visual <- DF_FG_VisualRobot %>% filter(source=='visual') %>% 
  pivot_wider(names_from = 'Label', values_from = 'Cover')

CM_FG_Robot <- DF_FG_VisualRobot %>% filter(source=='robot') %>% 
  pivot_wider(names_from = 'Label', values_from = 'Cover')

```


Calculate Bray-Curtis

```{r}
## calculate BC index
nLabels <- ncol(CM_FG_Visual)

BC_FGVR <- data.frame(Country=character(), Site=character(), Strata=character(), BC=numeric())
for (i in 1:nrow(CM_FG_Visual)){
  robotIndex <- which(CM_FG_Robot$Name==CM_FG_Visual$Name[i])
  if (length(robotIndex) > 0 ){
    CM_one <- bind_rows(CM_FG_Visual[i,6:nLabels], CM_FG_Robot[robotIndex,6:nLabels])
    CM_one[is.na(CM_one)] <- 0
    BC_FGVR <- bind_rows(BC_FGVR, 
                    data.frame(Country = CM_FG_Visual$country[i],
                               Site = CM_FG_Visual$site[i],
                               Strata = CM_FG_Visual$strata[i],
                               BC = as.numeric(vegdist(CM_one, na.rm = T))))
  }else {
    print(paste0("NOT FOUND in Robot: ", CM_FG_Visual$Name[i]))
  }
}
BC_FGVR$Site <- recode_factor(BC_FGVR$Site, PC="Punta Cuevas", PE="Punta Este", PL="Punta Lobos", 
                            LM="La Mancora", LV="La Ventana", PV="Playa Verde", 
                            CD="Charles Darwin Station", RA="Ratonera", TO="Tortuga Bay", 
                            MAMH="MAMH", MAPH="MAPH", MECH="MECH", MEGS="MEGS")
BC_FGVR$Strata <- factor(BC_FGVR$Strata, levels = c("LT", "MT", "HT"), labels = c("LOWTIDE", "MIDTIDE", "HIGHTIDE"))
BC_FGVR$Country <- factor(BC_FGVR$Country, levels = c("AR", "CO", "EC"), labels = c("ARGENTINA", "COLOMBIA", "ECUADOR"))

```

Summarise the BS distances by groups

```{r}
BCsummary <- BC_FGVR %>% group_by(Strata) %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummary, digits=3, caption = "Functional groups: VISUAL vs. ROBOT") %>% kable_styling("striped")


## global stats
BCsummaryGlobal <- BC_FGVR %>% 
  summarise(BCmean = mean(BC),
            BCsd = sd(BC), 
            BCq25 = quantile(BC, 0.25),
            BCq50 = quantile(BC, 0.50),
            BCq74 = quantile(BC, 0.75),
            BCmin = min(BC),
            BCmax = max(BC))

kable(BCsummaryGlobal, digits=3, caption = "Functional groups: VISUAL vs ROBOT global BC stats") %>% kable_styling("striped")

```


PLOTs

```{r}
pp_ARG <- ggplot(BC_FGVR %>% filter(Country=="ARGENTINA"), aes(Strata, BC))
pp_ARG <- pp_ARG + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) +
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ARGENTINA", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_COL <- ggplot(BC_FGVR %>% filter(Country=="COLOMBIA"), aes(Strata, BC))
pp_COL <- pp_COL + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="COLOMBIA", x="", y=" ") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ECU <- ggplot(BC_FGVR %>% filter(Country=="ECUADOR"), aes(Strata, BC))
pp_ECU <- pp_ECU + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", outlier.size = 0.3, lwd=0.2) + 
  ylim(0,0.6) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  labs(title="ECUADOR", x="", y="Bray-Curtis distance") +
  facet_grid(~Site) + 
  theme_pubclean() + 
  theme(legend.position = 'none')

pp_ARG / pp_COL / pp_ECU
```


Let's try another version

```{r}
pp <- ggplot(BC_FGVR, aes(Country, BC, fill=Strata))
pp + geom_boxplot(width=0.5, aes(fill=Strata), colour="black", position=position_dodge2(preserve="single") , outlier.size = 0.3, lwd=0.2) + 
  scale_color_manual(values = strataColor, aesthetics = 'fill') + 
  ylim(0, 0.3) + 
  labs(x="", y="Bray-Curtis Distance") + 
  facet_grid(~Strata) + 
  theme_pubclean()

```


GML model 




```{r}
## prepare data
BC_FGVR <- BC_FGVR %>% group_by(Country, Site, Strata) %>% mutate(Quadrat = seq_len(n()))

```


Full model

```{r}
model = glm(BC ~ Country*Strata, data=BC_FGVR, family=binomial)
summary(model)

testCountry = glht(model, linfct = mcp("Country" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))

testCountry = glht(model, linfct = mcp("Strata" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```




By STRATUM

HIGHTIDE 

```{r}


model = glm(BC ~ Country, data=BC_FGVR, subset = Strata=="HIGHTIDE", family=binomial)
summary(model)

testCountry = glht(model, linfct = mcp("Country" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```


MIDTIDE 

```{r}
model = glm(BC ~ Country, data=BC_FGVR, subset = Strata=="MIDTIDE", family=binomial)
summary(model)

testCountry = glht(model, linfct = mcp("Country" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```

LOWTIDE


```{r}
model = glm(BC ~ Country, data=BC_FGVR, subset = Strata=="LOWTIDE", family=binomial)
summary(model)

testCountry = glht(model, linfct = mcp("Country" = "Tukey"))
summary(testCountry)
plot(confint(testCountry))
```



```{r}
BCmean <- round(mean(BC_FGVR$BC),3)
BCn <- nrow(BC_FGVR)
BCsd <- sd(BC_FGVR$BC)
BCmargin <- qt(0.975,df=BCn-1)*BCsd/sqrt(BCn)
BCupper <- round(BCmean + BCmargin, 3)
BClower <- round(BCmean - BCmargin, 3) 

```

AS demonstrated, the classifier is insensitive to the variability produced by Country, Site and Strata, being equally efficient no matter the source of the quadrat. **In general, the difference between the classifier and the visual estimate of the community cover of a mean quadrat is `r BCmean` with a 95% confidence interval of [`r BClower` - `r BCupper`]**




